\begin{enumerate}
	\item An item of clothing is picked at random from one of two drawers in a dark room. The first drawer ($D_1$) contains 6 socks and 6 ties, and the other ($D_2$) contains 2 socks and 4 handkerchiefs. What is the probability that the item comes from the first drawer if it turns out to be a sock?\\
	Assuming the drawers are equally likely to be picked.
	\begin{align*}
		P(\n{sock}|D_1)=\frac{6}{6+6}=\frac12 &&
		P(\n{sock}|D_2)=\frac{2}{2+4}=\frac{1}{3}	
	\end{align*}
	$$P(\n{sock})=P(\n{sock}|D_1)\times P(D_1) + P(\n{sock}|D_2)\times P(D_2)=1/2\times1/2 +1/2\times1/3=\frac{5}{12}$$
	Hence,
	$$P(D_1|\n{sock})=\frac{P(\n{sock}\cap D_1)}{P(\n{sock})}
		=\frac{1/2\times1/2}{5/12}=\frac{3}{5}$$

	\item Suppose it is known that 1\% of the population suffers from a particular disease ($D$). A blood test has a 97\% chance of identifying the disease for diseased individuals, but also has a 6\% chance of falsely indicating that a healthy person has the disease.\\
	To summary:
	\begin{align*}
		P(D)=0.01 && P(+|D)=0.97 && P(+|D')=0.06	
	\end{align*}
	\begin{enumerate}
		\item What is the probability that a person will have a positive blood test?
		$$P(+)=P(+|D)P(D)+P(+|D')P(D') 
		=0.01\times0.97+0.99\times0.06=0.0691$$

		\item If your blood test is positive, what is the chance that you have the disease?
		$$P(D|+)=\frac{P(+|D)P(D)}{P(+)}
		=\frac{0.01\times0.97}{0.0691}=\frac{97}{691}\approx0.1404$$

		\item If your blood test is negative, what is the chance that you do not have the disease?
		\begin{align*}
			P(-|D')=1-0.06=0.94 && P(-)=0.01\times0.03+0.99\times0.94=0.9309
		\end{align*}
		Hence
		$$P(D'|-)=\frac{0.99\times0.94}{0.9309}=\frac{0.9306}{0.9309}=\frac{9306}{9309}\approx0.99968$$
	\end{enumerate}

	\item The weather on a particular day is classified as either cold, warm or hot. There is a probability of 0.15 that it is cold and a probability of 0.25 that it is warm. In addition, on each day it may either rain or not rain. On cold days there is a probability of 0.3 that it will rain, on warm days there is a probability of 0.4 that it will rain, and on hot days there is a probability of 0.5 that it will rain. If it is not raining on a particular day, what is the probability that it is cold?
	
	\begin{multline*}
		P(\n{no rain})=0.15\times(1-0.3)+0.25\times(1-0.4)+0.60\times(1-0.5)\\
			=0.15\times0.7+0.25\times0.6+0.60\times0.5=0.105+0.15+0.30=0.555
	\end{multline*}
	Hence,
	\[
		P(\n{cold}|\n{no rain})=\frac{P(\n{no rain}|\n{cold})P(\n{cold})}{P(\n{no rain})}
		=\frac{0.7\times0.15}{0.555}=\frac{0.105}{0.555}=\frac{7}{37}\approx0.18919.
	\]

	\item You have two coins, a fair one with probability of heads $\frac12$ and an unfair one with probability of heads $\frac13$ , but otherwise identical. A coin is selected at random and tossed, falling heads up. How likely is it that it is the fair one?
	$$
		P(\n{fair}|\n{head})=\frac{P(\n{head}|\n{fair})P(\n{fair})}{P(\n{head}|\n{fair})P(\n{fair})+P(\n{head}|\n{unfair})P(\n{unfair})}
		=\frac{1/2\times1/2}{1/2\times1/2+1/3\times1/2}=\frac{3}{5}
	$$

	\item Are the following statements true or false?
	\begin{enumerate}
		\item If a fair coin is tossed three times, the probability of obtaining two heads and one tail is the same as the probability of obtaining one head and two tails.\\
		\textbf{True}. Each outcome has probability $1/8$. Number of outcome with two heads = ${3\choose2}=3$, for one head = ${3\choose1}=3$. Thus both probabilities are $3/8$.

		\item If a card is drawn at random from a deck of cards, the probability that it is a heart increases if it is conditioned on the knowledge that it is an ace.\\
		\textbf{False} $P(\n{heart})=1/4$. $P(\n{heart}|\n{ace})=\frac{P(\n{heart}\cap\n{ace})}{P(\n{ace})}=\frac{1/52}{4/52}=\tfrac14$.

		\item If two events are independent, then the probability that they both occur can be calculated by multiplying their individual probabilities.\\
		\textbf{True}. This is the definition of independence: $P(A\cap B)=P(A)P(B)$.
		
		\item It is always true that $P(A|B)+P(A'|B)=1$.\\
		\textbf{True}. $P(A|B)+P(A'|B)=P((A\cup A')|B)=P(\Omega|B)=1$.

		\item It is always true that $P(A|B)+P(A|B')=1$.\\
		\textbf{False}. If $A$ never occurs and $B\ne\emptyset$ and $B\ne\Omega$ then $P(A|B)+P(A|B')=0$.

		\item It is always true that $P(A|B)\le P(A)$.\\
		\textbf{False}. If $B$ is $A$ and $0<P(A)<1$ then $P(A|B) = P(A|A) = 1 > P(A)$  
	\end{enumerate}
\end{enumerate}